---
title: "SimpLinVignette"
author: "Karissa Palmer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SimpLinVignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SimpLin)
```


## Package Description

The package \texttt{SimpLin} utilizes Rcpp/RcppArmadillo to perform simple linear regression (SLR) on two input vectors, $\mathbf{x}$ and $\mathbf{y}$. 

## Installation

The package is available for installation via the author's Github account. Users may utilize the below code to install the package.

```{r, eval = FALSE}
require(devtools)
install_github("KarissaPalmer/STAT600/Homework1/SimpLin", build_vignettes = TRUE)
library(SimpLin)
```

## Using the Package

What follows is a short tutorial on how to use the package \texttt{SimpLin}. An important note for users to remember is that the package will only take $n \times 1$ vectors as input and the vectors must be of the same length, as well as be numeric. The model that we are trying to fit with this package is always 
\begin{align*}
y &= \beta_0+\beta_1 x+\epsilon
\end{align*}

Moving to the example, we use the data set \texttt{mtcars} and will create a SLR model between horsepower and miles per gallon (mpg).

```{r}
data(mtcars)
head(mtcars, n = 3)
```
We may visualize the relationship between horsepower and mpg below. 

```{r, fig.width=6, fig.height=6}
plot(mtcars$hp, mtcars$mpg)
```

Now, to use \texttt{SimpLin}, we use the function within the package \texttt{SimpLinR}. It will output the estimated regression coefficients for $\beta_0$ and $\beta_1$, as well as their standard errors and 95% confidence intervals, residuals, and predicted values all as a list. We have

```{r}
mod_output<- SimpLinR(x = mtcars$hp, y = mtcars$mpg)
```


We may access each element of the list to create plots, tables, or do other analysis. For example, the confidence intervals and standard errors of $\beta_0$ and $\beta_1$ can be accessed as follows.  


```{r}
mod_output$Conf_Ints
mod_output$SEs
```

We have that the estimates for $\beta_0$ and $\beta_1$ themselves are  


```{r}
mod_output$Coefficients
```

which indicates that the line of best fit (LOBF) is 

\begin{align*}
\hat{y} &= 30.0989+(-0.0682)x
\end{align*}

Plotting the residuals, below.


```{r, fig.width=6, fig.height=6}
plot(mtcars$hp, mod_output$Residuals)
```


The predicted values along with the true values.


```{r, fig.width=6, fig.height=6}
plot(mtcars$hp, mtcars$mpg, col = 'red')
points(mtcars$hp, mod_output$Pred_Vals, col = 'blue')
```


## Troubleshooting

As mentioned earlier in the document, users must make sure that the vectors input in the function \texttt{SimpLinR} are of the same length and are numeric. To demonstrate the errors that users may see if either of these are violated by the input, we have the following.


```{r, error = TRUE}
#Vectors of different lengths
SimpLinR(x = c(1,1), y = c(1))

#Non-numeric entries in a vector
SimpLinR(x = c(1,1), y = c(1, 'b'))
```